\section{Timeline}
% "Cointegration shared" ≈ long-term equilibrium
% "Cointegration correlated" ≈ Correlation in short-term behavior ≈ short-term dynamics

\begin{frame}{Timeline}
	\begin{center}
		\begin{tikzpicture}
			% Timeline line
			\draw[thick] (0,0) -- (8,0);
			
			% Events
			\foreach \x/\year/\label in {0/\small Week 1/\small Kickoff, 2/\small Week 2/\small Stationarity, 4/\small Week 3/\small Johansen, 6/\small Week 4/\small ECM, 8/\small Week 5/\small Wrap-up} {
				\draw[fill=ritsumeikan] (\x,0) circle (4pt);
				\node[above] at (\x,0.2) {\textbf{\year}};
				\node[below] at (\x,-0.2) {\label};
			}
		\end{tikzpicture}
	\end{center}
\end{frame}

\begin{frame}{Week 1}
	\textbf{Period: }(Oct 7 – Oct 13)
	\begin{itemize}
		\item Team discussion \& work distribution (who handles dataset search, coding, slides, etc.).
		\item Finalize dataset (e.g., macroeconomic/financial variables).
		\item Everyone revises basics: stationarity, ADF/PP tests, cointegration concept.
	\end{itemize}
\end{frame}

\begin{frame}{Week 2}
	\textbf{Period: }(Oct 14 – Oct 20)
	\begin{itemize}
		\item Perform unit root tests (ADF/PP) on chosen variables.
		\item Share results among team \& discuss division of analysis.
		\item Start applying Engle–Granger 2-step test for initial cointegration check.
	\end{itemize}
\end{frame}

\begin{frame}{Week 3}
	\textbf{Period: }(Oct 21 – Oct 27)
	\begin{itemize}
		\item Run Johansen cointegration test for multiple series.
		\item Identify cointegrating vectors \& interpret results.
		\item Team sync-up: assign one subgroup to results interpretation and one to visuals/plots.
	\end{itemize}
\end{frame}

\begin{frame}{Week 4}
	\textbf{Period: }(Oct 28 – Nov 3)
	\begin{itemize}
		\item Develop Error Correction Model (ECM) to show short-run vs long-run dynamics.
		\item Validate with diagnostic checks and finalize output tables/graphs.
		\item Start making presentation slides (intro, methodology, results, discussion).
	\end{itemize}
\end{frame}

\begin{frame}{Week 5}
	\textbf{Period: }(Nov 4 – Nov 7)
	\begin{itemize}
		\item Team discussion \& rehearsal: combine slides from all members.
		\item Final check: clarity, timing, flow of presentation.
		\item Submit final slides/report if required.
		\item Practice dry run before presentation day.
	\end{itemize}
\end{frame}